Fast Bayesian Inference for Exoplanet Discovery in Radial Velocity Data

### 2014-11-13 Paper/ms.tex
Some more work

\section{Orbit Simulations}\label{sec:orbits}
The expected (noise-free) signal due to an exoplanet is periodic, but
non-sinusoidal when the orbit is not perfectly circular. The expected
shape $m(t)$ of the variations can be obtained from mechanical considerations.
To save time, we pre-computed the properties of orbits as a function of
ellipticity. We also made the standard assumption that the planets do not
interact, so the expected signal due to several planets is the sum of the
contributions of each planet.

@@

@@

The marginal likelihood was $\ln(\mathcal{Z}) \approx -217.04$ and the
information was $\mathcal{H} \approx 80.0$ nats.

>>>>

\section{Orbit Simulations}\label{sec:orbits}
The expected (noise-free) signal due to an exoplanet is periodic, but
non-sinusoidal when the orbit is not perfectly circular. The expected
shape $m(t)$ of the variations is needed in order to evaluate the likelihood
function for any proposed setting of the parameters.
To save time, we pre-computed the properties of orbits as a function of
ellipticity. We also made the standard assumption that the planets do not
interact, so the expected signal due to several planets is the sum of the
contributions of each planet.

@@

By precomputing a set of orbits before running the MCMC, we are able to
do of order 10,000 likelihood evaluations per second per CPU core.

@@

The marginal likelihood for our model was
$\ln(\mathcal{Z}) \approx -217.04$ and the information
(Kullback-Leibler divergence from the prior to the posterior)
was $\mathcal{H} \approx 80.0$ nats.
